Exercise 2: Quality Attributes and Architectural Design of the HS07 System

### 2008-02-25 trunk/SAiP/Module1/H2/paper.tex
Added the figures.

@@

>>>>

\section{Packages}

\begin{figure}[!htb]
\centerline{\epsfig{figure="figures/mv-model",scale=0.8 }}
\caption{Module View of the web interface in the redesigned HS07 system}
\label{fig:mv-model}
\end{figure}

\begin{figure}[!htb]
\centerline{\epsfig{figure="figures/mv-factory",scale=0.8 }}
\caption{Module View of the abstract factory in the redesigned HS07 system}
\label{fig:mv-factory}
\end{figure}

@@

\section{Sequence Diagrams}

\begin{figure}[!htb]
\centerline{\epsfig{figure="figures/seq-stt",scale=0.8 }}
\caption{Sequence Diagram for the web requests in the redesigned HS07 system}
\label{fig:seq-stt}
\end{figure}

\begin{figure}[!htb]
\centerline{\epsfig{figure="figures/seq-tfac",scale=0.8 }}
\caption{Sequence Diagram for the Abstract Factory in the redesigned HS07 system}
\label{fig:seq-tfac}
\end{figure}

\section{Deployment}

\begin{figure}[!htb]
\centerline{\epsfig{figure="figures/deployment",scale=0.8 }}
\caption{Deployment in the redesigned HS07 system}
\label{fig:deployment}
\end{figure}
